---
output: 
    html_document:
        keep_md: true
        fig_width: 10
        fig_height: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "vignettes/")
```

# jcolors

[![Build Status](https://travis-ci.org/jaredhuling/jcolors.svg?branch=master)](https://travis-ci.org/jaredhuling/jcolors)

`jcolors` contains a selection of `ggplot2` color palettes that I like

## Installation


Install `jcolors` from GitHub:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("jaredhuling/jcolors")
```

Access the `jcolors` color palettes with `jcolors()`:

```{r eval = TRUE, message = FALSE, warning = FALSE}
library(jcolors)

jcolors('default')

```

## All available palettes

```{r displayall}
display_all_jcolors()
```

## Use with `ggplot2`

Now use `scale_color_jcolors()` with `ggplot2`:

```{r eval = TRUE, message = FALSE, warning = FALSE}
library(ggplot2)
library(gridExtra)

data(morley)

pltl <- ggplot(data = morley, aes(x = Run, y = Speed,
group = factor(Expt),
colour = factor(Expt))) +
    geom_line(size = 2) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey97"),
          panel.border = element_blank(),
          legend.position = "bottom")

pltd <- ggplot(data = morley, aes(x = Run, y = Speed,
group = factor(Expt),
colour = factor(Expt))) +
    geom_line(size = 2) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey15"),
          legend.key = element_rect(fill = "grey15"),
          panel.border = element_blank(),
          panel.grid.major = element_line(color = "grey45"),
          panel.grid.minor = element_line(color = "grey25"),
          legend.position = "bottom")

grid.arrange(pltl + scale_color_jcolors(palette = "default"),
             pltd + scale_color_jcolors(palette = "default"), ncol = 2)

grid.arrange(pltl + scale_color_jcolors(palette = "pal2"),
             pltd + scale_color_jcolors(palette = "pal2"), ncol = 2)



```

Color palettes can be displayed using `display_jcolors()`

## default
```{r}
display_jcolors("default")
```

## pal2
```{r}
display_jcolors("pal2")
```

## pal3
```{r}
display_jcolors("pal3")
```

## pal4
```{r}
display_jcolors("pal4")
```

## pal5
```{r}
display_jcolors("pal5")
```

## pal6
```{r}
display_jcolors("pal6")
```

## rainbow
```{r}
display_jcolors("rainbow")
```




More example plots

```{r moreplots}
grid.arrange(pltl + scale_color_jcolors(palette = "pal3"),
             pltd + scale_color_jcolors(palette = "pal3"), ncol = 2)

grid.arrange(pltl + scale_color_jcolors(palette = "pal4"),
             pltd + scale_color_jcolors(palette = "pal4") + 
                 theme(panel.background = element_rect(fill = "grey5")), ncol = 2)

grid.arrange(pltl + scale_color_jcolors(palette = "pal5"),
             pltd + scale_color_jcolors(palette = "pal5"), ncol = 2)


pltd <- ggplot(data = OrchardSprays, aes(x = rowpos, y = decrease,
group = factor(treatment),
colour = factor(treatment))) +
    geom_line(size = 2) +
    geom_point(size = 4) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey15"),
          legend.key = element_rect(fill = "grey15"),
          panel.border = element_blank(),
          panel.grid.major = element_line(color = "grey45"),
          panel.grid.minor = element_line(color = "grey25"),
          legend.position = "bottom")


pltd + scale_color_jcolors(palette = "pal6")

```

## Continuous Color Palettes

```{r mountain_ex, fig.height=6}
set.seed(42)
plt <- ggplot(data.frame(x = rnorm(10000), y = rexp(10000, 1.5)), aes(x = x, y = y)) +
      geom_hex() + coord_fixed() + theme(legend.position = "bottom")

plt2 <- plt + scale_fill_jcolors_contin("pal2", bias = 1.75) + theme_bw()
plt3 <- plt + scale_fill_jcolors_contin("pal3", reverse = TRUE, bias = 2.25) + theme_bw()
grid.arrange(plt2, plt3, ncol = 2)
```

```{r contin_example}
colfunc  <- jcolors_contin()
jcols    <- colfunc(1000)
n        <- length(jcols)

colfunc2 <- jcolors_contin("pal2")
jcols2   <- colfunc2(1000)

colfunc3 <- jcolors_contin("pal3")
jcols3   <- colfunc3(1000)

colfuncr <- jcolors_contin("rainbow")
jcolsr   <- colfuncr(1000)

par(mfrow = c(4,1), mai = c(0.1, 0.1, 0.1, 0.1))
image(1:n, 1, as.matrix(1:n),
      col  = jcols,
      xlab = "", ylab = "",
      xaxt = "n", yaxt = "n", bty = "n")
image(1:n, 1, as.matrix(1:n),
      col  = jcols2,
      xlab = "", ylab = "",
      xaxt = "n", yaxt = "n", bty = "n")
image(1:n, 1, as.matrix(1:n),
      col  = jcols3,
      xlab = "", ylab = "",
      xaxt = "n", yaxt = "n", bty = "n")
image(1:n, 1, as.matrix(1:n),
      col  = jcolsr,
      xlab = "", ylab = "",
      xaxt = "n", yaxt = "n", bty = "n")
```




